---
title: "TSRC Provincial Tourism Exploration"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(chorddiag)
library(treemap)
library(d3treeR)

# Matrix with data exclusive of same-province visits
o_e <- matrix(c(0,9,64,26,33,112,2,0,17,21,
              7,0,121,114,14,32,0,0,8,3,
              57,226,0,402,57,197,6,13,46,55,
              10,105,363,0,147,141,8,2,14,14,
              34,42,57,208,0,2181,44,13,64,128,
              165,133,240,273,2848,0,241,69,571,587,
              6,3,12,8,34,407,0,251,215,118,
              9,3,8,4,25,119,198,0,882,210,
              46,7,62,11,48,403,104,554,0,2531,
              11,17,46,19,94,432,57,104,1035,0),
            byrow = TRUE,
            nrow = 10, ncol = 10)

# Matrix with data inclusive of same-province visits
o_i <- matrix(c(1360,9,64,26,33,112,2,0,17,21,
                7,129,121,114,14,32,0,0,8,3,
                57,226,1977,402,57,197,6,13,46,55,
                10,105,363,1312,147,141,8,2,14,14,
                34,42,57,208,24742,2181,44,13,64,128,
                165,133,240,273,2848,38875,241,69,571,587,
                6,3,12,8,34,407,2285,251,215,118,
                9,3,8,4,25,119,198,3478,882,210,
                46,7,62,11,48,403,104,554,8333,2531,
                11,17,46,19,94,432,57,104,1035,10557),
              byrow = TRUE,
              nrow = 10, ncol = 10)

provinces <- c("NL","PEI","NS","NB","QC","ON","MB","SK","AB","BC")

dimnames(o_e) <- list(origin = provinces, destination = provinces)
dimnames(o_i) <- list(origin = provinces, destination = provinces)

colours <- RColorBrewer::brewer.pal(10, "BrBG")

# Treemap

prov_exp <- read_csv("provincial-overnight-expenditures.csv")


tm <-treemap(prov_exp,
             index=c("Province","Type"),
             vSize="Expenditure",
             vColor="Province",
             type="categorical")

```

### Flows of overnight tourist arrivals between Canadian provinces. {data-width=800}
    
```{r}
d3tree2(tm, rootname = "Province")

```
  
***

Source: Travel Survey of Residents of Canada 2014, Statistics Canada. Weighted data. Interprovincial flows are rounded to and represented in 1,000s.

Catalogue #: SK-TAB#6-PRV

Chord-diagram based on Mike Bostock's D3.js work (https://bl.ocks.org/mbostock/4062006) and implemented using htmlwidgets and chorddiag R packages (https://github.com/mattflor/chorddiag).
    
### Value of expenditures by overnight tourists in each province broken down by category {data-width=800}

```{r}
chorddiag(o_e, 
          groupnamePadding = 30, 
          groupColors = colours,
          tickInterval = 100,
          chordedgeColor = "darkgrey",
          groupedgeColor = "darkgrey",
          groupThickness = 0.075)

```

***
Source: Travel Survey of Residents of Canada 2014, Statistics Canada. Weighted data. Reallocated expenditures are represented in $1,000s. 

Catalogue #: SK-TAB#8-PRE

Interactive treemap based on Mike Bostock's D3.js work (https://bost.ocks.org/mike/treemap/) and implemented using htmlwidgets and d3treeR R packages (https://github.com/timelyportfolio/d3treeR).

### Chart 3

```{r}

```

